---
title: "Spawning Designation"
output: html_notebook
---

Attempting to classify striped bass according to location during presumed spawning. Rules are:

* **Potomac** if
    + Detected between Mar 15 and May 15 *and*
    + Above Rt 301 ("Upper Potomac" array)
*  **Delaware** if
    + Detected between Mar 15 and May 15 *and*
    + Above RKM 50 of Delaware river
        * Smyrna latitude is 39? 18' 21.37"N so using sites N of this location
*  **Hudson** if
    + Detected between Apr 15 and Jun 15 *and*
    + Above RKM 60 of Hudson River
        * Tappan Zee Br latitude is 41? 4' 11.73"N, so using sites N of this location
*  **Skipped spawning** if alive, but not located in one of these arrays

# Find which sites fit the rule
## Dates
First, we need to label the period that the fish was alive. Here, determined as the time between the first and the most-recent detection.
```{r, message = F, warning = F}
load('p:/obrien/biotelemetry/past sb/past-analysis/secor.sb.rda')
library(dplyr)
secor.sb <- secor.sb %>% 
  group_by(transmitter) %>% 
  summarize(dmin = min(date.local),
            dmax = max(date.local)) %>% 
  left_join(secor.sb)
```


Next, need to categorize the dates. To be year agnostic, it's easiest to use the day of year for each date as a filter. I'll just ignore leap years for this.
```{r, message = F, warning = F}
library(lubridate)
```
March 15 (Potomac and Delaware): `lubridate::yday('2014/03/15') = ` `r yday('2014/03/15')`

May 15 (Potomac and Delaware): `r yday('2014/05/15')`

April 15 (Hudson): `r yday('2014/04/15')`

June 15 (Hudson): `r yday('2014/06/15')`


## Sites
I've pre-coded most of the sites into arrays. Potomac is already listed as "Upper Potomac", but I need to find the sites that pass the rule in DE and Hudson.

```{r}
dets <- secor.sb %>% 
  filter(grepl('-25', transmitter)) %>% 
  mutate(doy = lubridate::yday(date.local),
         year = lubridate::year(date.local))
hud <- dets %>% 
  filter(array == 'Hudson',
         lat >= 41.069925,
         doy >= 105,
         doy <= 166)
del <- dets %>% 
  filter(array == 'Delaware',
         lat >= 39.30594,
         doy >= 74,
         doy <= 135)
pot <- dets %>% 
  filter(array == 'Upper Potomac',
         doy >= 74,
         doy <= 135)

dets <- pot %>% 
  rbind(hud) %>% 
  rbind(del)
```
To judge skipped spawning, we need to make sure that all years are accounted for in the data set.
```{r}
dets <- dets %>% 
  left_join(data.frame(transmitter = rep(paste0('A69-1601-', 25434:25533),
                                         each = 4),
                       year = rep(2014:2017, times = 100)))
```


Now we know the "life" of each fish (we can tell if there was skipped spawning), and have filtered down to the dates/sites we're interested in.
```{r}
dets %>% 
  group_by(transmitter, year) %>% 
  distinct(array)
```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

